TRITON: Globally Consistent Sim-to-Real Transfer ``I can't believe it's not real!"

### 2022-06-08 CORL/example.tex
Added a bunch of TODO items and fixed syntax

@@

\begin{equation}
	\label{eq:somename}
	Do stuff like this

\end{equation}

@@

@@

	Each neural texture $\tau_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
	Given a two-dimensional $uv$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for the MLP.
	\makebox[\textwidth]
	{
		$
		\tau_i(uv) = 
		\
		M_i\left(\left[
			\sin f_1 uv, \ 
			\cos f_1 uv, \ 
			\sin f_2 uv, \ 
			\cos f_2 uv, \ 
			\dots \ 
			\sin f_{256} uv, \ 
			\cos f_{256} uv \ 
		\right]\right)
		$
	}
	where $uv$ and $f_i \in N_{ormal}(\mu=0,\ \sigma=10)$ are two dimensional vectors,
	 $f_i uv$ represents their dot product, 
	%  $rgb$ represents a 3d color vector,
	 and $M_i$ maps a $uv$ embedding to an $rgb$ color value:
	 $M_i: \mathbb{R}^{256} \rightarrow \mathbb{R}^3$.
	Note that there is nothing special about 256 or 10: these hyperparameter values just happen to work nicely.

>>>>

TODO: Add UV to the fourier feature diagram.

@@

@@

	TODO: Put summary of section here

@@

	Each neural texture $\tau_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
	Given a two-dimensional $uv$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for the MLP.
	\begin{equation}
			\tau_i(uv) = 
			\
			M_i\left(\left[
				\sin f_1 uv, \ 
				\cos f_1 uv, \ 
				\sin f_2 uv, \ 
				\cos f_2 uv, \ 
				\dots \ 
				\sin f_{256} uv, \ 
				\cos f_{256} uv \ 
			\right]\right)
	\end{equation}
	where $uv$ and $f_i \in N_{ormal}(\mu=0,\ \sigma=10)$ are two dimensional vectors,
	 $f_i uv$ represents their dot product, 
	%  $rgb$ represents a 3d color vector,
	 and $M_i$ maps a $uv$ embedding to an $rgb$ color value:
	 $M_i: \mathbb{R}^{256} \rightarrow \mathbb{R}^3$.
	Note that there is nothing special about 256 or 10: these hyperparameter values just happen to work nicely.
